\documentclass{article}
\usepackage{blindtext}
\usepackage{ragged2e}
\usepackage{fancyvrb}


\title{Tarea 4: Ejercicios PROC}
\author{Daniel Rubén Ochoa Galván}
\begin{document}
\maketitle
\begin{center}
	Lenguajes de Programación
\end{center}

Exercise 3.20. [$\star$] In PROC, procedures have only one argument, but one can get the effect of multiple argument procedures by using procedures that return other procedures. For example, one might write code like

\begin{Verbatim}
	let f = proc (x) proc (y) ...
	in ((f 3) 4)
\end{Verbatim}

This trick is called \emph{Currying}, and the procedure is said to be \emph{Curried}. Write a Curried procedure that takes two arguments and returns their sum. You can write $x + y$ in our language by writing $-(x, -(0, y))$.


\begin{Verbatim}[fontfamily=helvetica, frame=lines]
		let suma = proc (x) proc (y) -(x, -(0, y)) ...
\end{Verbatim}

Exercise 3.27 [$\star$] Add a new kind of procedure called a \texttt{traceproc} to the language. A \texttt{traceproc} works exactly like a \texttt{proc}, except that it prints a trace message on entry and on exit. \\
Extendiendo el lenguaje agregando a la sintaxis concreta:
\begin{center}
\emph{Expression}  ::=  \texttt{traceproc} (\emph{Identifier}) \emph{Expression}
\end{center}
Extendiendo el lenguaje agregando a la sintaxis abstracta:
\begin{center}
(traceproc-exp \emph{var} \emph{body})
\end{center}
Especificando la semántica:
\begin{Verbatim}[fontfamily=helvetica, frame=topline]
	(value-of (proc-exp var body) env)
	   = (proc-val (procedure var body env))
\end{Verbatim}
\emph{donde:}
\begin{Verbatim}[fontfamily=helvetica, frame=bottomline]
	(apply-procedure (procedure var body env) val)
	   = (value-of body [var = val] env)
\end{Verbatim}
Modificando la implementación de \texttt{apply-procedure} para integrar la especificación de \texttt{traceproc}:

\begin{Verbatim}[fontfamily=helvetica, frame=lines]
(define (apply-procedure proc val)
  (unless (procedure? proc)
    (error 'value-of "no es un procedimiento: ~e" proc))
  (let ([var (procedure-var proc)]
        [body (procedure-body proc)]
        [saved-env (procedure-saved-env proc)])
    (cond
      [(traceproc-exp? proc)
       (display ("Entrando a proc..."))
       (value-of body (extend-env var val saved-env))
       (display ("Saliendo de proc..."))]
      [(proc-exp? proc)
       (value-of body (extend-env var val saved-env))])))
\end{Verbatim}


\end{document}
